GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-10-07 paper/kbanotebook2013/content/discussion.tex

For slot extraction part, in order to improve the performance, what we need
are: 1) Using multi-class classifiers instead of pattern matching method to 
extract slot values in order to increase both recall and accuracy for slots
``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'',
``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different 
kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s 
inaccurate tags. The first and second tasks are the most important tasks we 
need to do.

About 50\% of twitter entities are missing. One reason could be 
that those entities are not very famous. For example Brenda Weiler google 
search result has 860,000 documents over the whole web. For our 
small portion of the web it might make sense. If you pay attention to the 
histogram of the entities found you'll note that more than half of the 
entities have appeared in less than 10 StreamItems. A good portion have 
appeared only once. Which the document does not necessarily have good 
information for us.

>>>>

For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to 
extract slot values in order to increase both recall and accuracy for slots
``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'',
``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different 
kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s 
inaccurate tags. The first and second tasks are the most important tasks we 
need to do.

About 50\% of twitter entities are not found by the system. One reason could be 
that those entities are not very famous. For example Brenda Weiler google 
search result has 860,000 documents over the whole web. For our 
small portion of the web it might make sense. If you pay attention to the 
histogram of the entities found you'll note that more than half of the 
entities have appeared in less than 10 StreamItems. A good portion have 
appeared only once. Which the document does not necessarily have good 
information for us.

### 2013-10-07 paper/kbanotebook2013/content/introduction.tex

@@

An important challenge in maintaining Wikipedia (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate. Currently, there is considerable time lag between the publication date of cited news articles and the date of an edit to WP creating the citation. As an example, the median time lag for a sample of about 60,000 web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail\cite{JFrank12}. It is also noted that the majority of Wikipedia entities have updates on their associated Wiki article much less frequently than their mention frequency. Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB. Further, the number of mentions is much larger than the number of entities\cite{JFrank12}.

For this track, assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}. Documents would be divided according to two metrics: 1) mentioning the entity or not, 2) relevance level to the entity:
\begin{itemize}
\item \textbf{Mention} 
\begin{itemize}
\item \textbf{Mention:} Document explicitly mentions target entity, such as full name, partial name, nickname, pseudonym, title, stage name.
\item \textbf{Zero-mention:} Document does not directly mention target. Could still be relevant, e.g. metonymic references like ``this administration'' -- \textgreater ``Obama''. See also synecdoche. A document could also be relevant to target entity through relation to entities mentioned in document -- apply this test question: can I learn something from this document about target entity using whatever other information I have about entity?
\end{itemize}
\item \textbf{Relevance}
\begin{itemize}
\item \textbf{Garbage:} not relevant, e.g. spam.
\item \textbf{Neutral:} Not relevant, i.e. no info could be deduced about entity, e.g., entity name used in product name, or only pertains to community of target such that no information could be learned about entity, although you can see how an automatic algorithm might have thought it was relevant.
\item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive implications, or topics or events of likely
impact on entity.
\item \textbf{Central:} Relates directly to target such that you would cite it in the WP article for this entity, e.g. entity is a
central figure in topics/events.

@@

\subsection{Streaming Slot Filling (SSF)}
The task is that given certain Wikipedia or Twitter entities 
(wiki/twitter URLs) and certain relations of interest (given in Table  \ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling). This can be used to automatically populate knowledgebases such as free-base or DBPedia 
or even fill-in the information boxes at Wikipedia. Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:

@@

\noindent Since this is \textit{streaming} slot filling, we are only interested in new 
slot values that were not substantiated earlier in the stream corpus. In Table \ref{table:slotNameOntology} you can view some slot values 
and their types, the comprehensive description of which can be found at
\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values. This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.

>>>>

An important challenge in maintaining Wikipedia.org (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate. Currently, there is considerable time lag between the publication date of cited news articles and the date of an edit to WP creating the citation. As an example, the median time lag for a sample of about 60,000 web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail\cite{JFrank12}. It is also noted that the majority of Wikipedia entities have updates on their associated Wiki article much less frequently than their mention frequency. Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB. Further, the number of mentions is much larger than the number of entities\cite{JFrank12}.

@@

For this track, assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}. Documents would be divided according to two metrics: a) mentioning the entity or not, b) relevance level to the entity:
\begin{itemize}
\item \textbf{Mention} 
\begin{itemize}
\item \textbf{Mention:} Document explicitly mentions target entity, such as full name, partial name, nickname, pseudonym, title, stage name.
\item \textbf{Zero-mention:} Document does not directly mention target. Could still be relevant, e.g. metonymic references like ``this administration'' -- \textgreater ``Obama''. See also synecdoche. A document could also be relevant to target entity through relation to entities mentioned in document -- apply this test question: can I learn something from this document about target entity using whatever other information I have about entity?
\end{itemize}
\item \textbf{Relevance}
\begin{itemize}
\item \textbf{Garbage:} not relevant, e.g. spam.
\item \textbf{Neutral:} Not relevant, i.e. no info could be deduced about entity, e.g., entity name used in product name, or only pertains to community of target such that no information could be learned about entity, although you can see how an automatic algorithm might have thought it was relevant.
\item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive implications, or topics or events of likely
impact on entity.
\item \textbf{Central:} Relates directly to target such that you would cite it in the WP article for this entity, e.g. entity is a
central figure in topics/events.

@@

\subsection{Streaming Slot Filling (SSF)}
The task is that given certain WP or Twitter entities 
(wiki/twitter URLs) and certain relations of interest (given in Table  \ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling). This can be used to automatically populate knowledgebases such as free-base or DBPedia 
or even fill-in the information boxes at Wikipedia. Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:

@@

\noindent In \textit{streaming} slot filling, we are only interested in new 
slot values that were not substantiated earlier in the stream corpus. In Table \ref{table:slotNameOntology} you can view some slot values 
and their types, the comprehensive description of which can be found at
\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values. This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.

### 2013-10-07 paper/kbanotebook2013/content/results.tex

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was composed of a single node cluster, which we refer to as the \textit{server}; the configuration of which is as described in Table \ref{table:serverspec}. The corpus is a snapshot of the web in English. Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}. Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations. This corpora consists of various media types the distribution of which can be found in \ref{table:documentsDist}. To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2013 is considered as training data. The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.

@@

\begin{table}
\caption{Benchmark Server Specifications }
\centering
\label{table:serverspec}
\begin{tabular}{|c|l|}
\hline 
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

@@

\begin{tabular}{|c|c|c|c|}
\hline 
 & Correct & Incorrect Entity name & Incorrect Value \\ 
\hline 
Sampling \#1 & 55\% & 17\% & 27\% \\ 
\hline Sampling \#2 & 54\% & 15\% & 31\%  \\ 
\hline 
\end{tabular} 
\end{table}

\begin{table}
\caption{Recall Measure on Submission Infer }
\centering
\label{table:finalresultrecall}
\begin{tabular}{|c|p{3cm}|p{4cm}|}
\hline 
 Slot Name & Total instances of slot value found & \# of entities covered by slot value \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\begin{table}
\caption{SSF Accuracy Measure on Submission Infer }
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|c|c|c|c|}
\hline 
 Slot Name  & Correct & Incorrect Entity name & Incorrect Value \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

>>>>

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was composed of a single node cluster, which we refer to as the \textit{server}; the configuration of which is as described in Table \ref{table:serverspec}. The corpus is a snapshot of the web in English. Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}. Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations. This corpora consists of various media types the distribution of which can be found in \ref{table:documentsDist}. To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2012 is considered as training data. The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.

@@

\begin{table}
\caption{Benchmark Server Specifications }
\centering
\label{table:serverspec}
\begin{tabular}{|c|l|}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

@@

\begin{tabular}{|c|c|c|c|}
\hline 
 & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Sampling \#1 & 55\% & 17\% & 27\% \\ 
\hline Sampling \#2 & 54\% & 15\% & 31\%  \\ 
\hline 
\end{tabular} 
\end{table}

\begin{table}
\caption{Recall Measure on Submission Infer }
\centering
\label{table:finalresultrecall}
\begin{tabular}{|c|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\begin{table}
\caption{SSF Accuracy Measure on Submission Infer }
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|c|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline
